\chapter{Improving the Security of the Meteor Stegosystem}
\label{chap:security}

When we communicate using a steganographic protocol, security is of utmost importance.
We probably communicate in an environment that is very hostile against its parties.
Therefore, we should satisfy the most rigorous security requirements we can.

In \autoref{def:sec-hopper}, we established the notion of steganographic security against chosen hiddentext attacks (SS-CHA).
In this chapter, we will show that the Meteor stegosystem is secure against SS-CHA adversaries with a query complexity of one, i.e., adversaries that are allowed to send up to one query to the encoding oracle.
Afterwards, we will argue that Meteor is insecure against adversaries with query complexity greater than one.
In conclusion, we will modify the Meteor stegosystem to improve its security against SS-CHA adversaries by replacing the one-time pad used in Meteor with a symmetric encryption scheme in counter mode (SES-CTR).

\section{Security Against Chosen Hiddentext Attackers}

In \autoref{def:sec-hopper}, we introduced Hopper's notion of steganographic security against chosen hiddentext attackers (SS-CHA).
In this chapter, we will show that the Meteor stegosystem is secure against ppt. SS-CHA adversaries with query complexity of one and insecure against ppt. SS-CHA adversaries with query complexity greater than one.


\begin{theorem}
  Meteor is secure against ppt. SS-CHA adversaries with query complexity of one.
\label{thm:meteor-secure}
\end{theorem}
\begin{proof}
  We show SS-CHA security by reduction to an attack against the underlying PRG.
  Let $\mathcal{A}$ be a ppt. SS-CHA attacker against the Meteor stegosystem, i.e., $\mathcal{A}$ can distinguish the output of $ST$, i.e., $Encode_{\mathcal{C}}^\beta$, from that of $CT$, an oracle randomly sampling from the RRRSS $\mathcal{C}$, with one query $(m,h)$.
  
  We will now show that $\mathcal{A}$ can be used to attack the PRG.
  For the given query $(m,h)$, the attacker gets the response $c = c_0 ||c_1 || \dots || c_{\tau}$ from $ST$ or $CT$, i.e., a stegotext from $Encode$ or a random sequence of samples from the RRRSS, respectively, depending on the challenger's random bit.
  The attacker can then use $Prefix$ and $LenPrefix$ (as Bob would during decoding) to recover the bit string $r$ used to sample from the channel, since these functions don't need the secret key $k$.

  How is $r$ constructed if the challenger used $ST$ to generate $c$?
  It is the exclusive-or of $\beta$ bits of $m$ and a pseudorandom value $mask$ from a PRG.
  Since $mask$ is pseudorandom, the exclusive-or of $mask$ and some other value is pseudorandom as well.
  To distinguish the output of $ST$ from that of $CT$, the attacker has to distinguish $r$ from a randomly sampled token, i.e., the attacker has to distinguish $r$ from a truly random value $r'$.
  Therefore, $\mathcal{A}$ can be used to attack the PRG.
  Since we expect the underlying PRG to be secure, $\mathcal{A}$ cannot distinguish $r$ from $r'$ with non-negligible probability in polynomial time.
\end{proof}

But is this sufficient to satisfy Hopper's definition of steganographic security?
Unfortunately not.
In Hopper's $(t,q,l)$-SS-CHA game, an attacker may perform up to $q(\lambda)$ queries.
The aforementioned security proof only considers security against one query.

\begin{theorem}
  Meteor is insecure against ppt. SS-CHA adversaries with query complexity greater than one.
\end{theorem}
\begin{proof}
Let $\mathcal{A}$ be an SS-CHA adversary with at least two queries.
Let $\mathcal{A}$ repeat the same query $(m,h)$ twice.
While the oracle $CT$ will~ --~ with overwhelming probability~ --~ sample an entirely different covertext from the distribution,  $ST$ will output the same stegotext twice.
After only two queries, $\mathcal{A}$ is able to distinguish Meteor's outputs from those of a random oracle with high certainty.

We can verify this using the Meteor online demo \cite{MeteorDemo2021}.
For example, let
\begin{lstlisting}
m = "Hello world"
h = "Despite a long history of research and wide-spread applications to censorship resistant systems, practical steganographic systems capable of embedding messages into realistic communication distributions, like text, do not exist.\n\n"
\end{lstlisting}
be a query to the Meteor online demo.
Besides a key, the Meteor online demo requires a nonce, which is neither part of the stegotext nor contained in the protocol, but has to be shared between participants.
Therefore, we expect the nonce to be part of the key.
For the sake of this example, let $k = (key, nonce)$ be given as follows:
\begin{lstlisting}
key   = 0x010101010101010101010101010101010101
          010101010101010101010101010101010101
nonce = 0x030303030303030303030303030303030303
          030303030303030303030303030303030303
\end{lstlisting}
The specific choice of $k$ is not relevant, as the Meteor stegosystem is deterministic for any $k$.
The stegotext generated for this combination $(k,m,h)$ is
\begin{lstlisting}
c = "- The great strength of steganography is the ability to send messages without any significant communication layer of encryption, Pinnew"
\end{lstlisting}
while random sampling from the distribution would -- with overwhelming probability -- yield a different covertext for each invocation of the encoding oracle.
Therefore, $\mathcal{A}$ has significant advantage against the stegosystem after two queries.
\end{proof}

In the following section, we will propose a modification to Meteor that improves the security against SS-CHA adversaries by randomizing the stegotext returned by $Encode$.

\section{Improving Meteor's Security Against Chosen Hiddentext Attackers}

To improve Meteor's security, we have to randomize the output of $Encode$, i.e., on each invocation with the same inputs $Encode$ should, with overwhelming probability, return a different stegotext while retaining indistinguishability from random sampling.

To achieve that we introduce a new cryptographic primitive, a symmetric encryption scheme in counter mode with a pseudorandom function $F$ (SES-CTR or simply $SES$).
We will introduce a definition of $SES$ which is equivalent to that introduced in \cite{Berndt2017}.
There, it is argued that $SES$ satisfies the IND\$-CPA property if $F$ is a secure pseudorandom function.

The idea behind encryption in $SES$ is simple:
First, split the message $m$ into $n$ blocks of size $F.in(\lambda)$.
Choose an $IV$ of size $F.in(\lambda)$ at random.
It is important not to reuse an $IV$ with a given key $k$ to retain one-time pad security.
Now, for each block $m_i$, use $F.Eval$ to generate a pseudorandom value $r = F.Eval(k, IV+i)$.
Afterwards, calculate the exclusive-or of $r$ and $m_i$ to get the next block $c_i$.
The ciphertext of size $(n+1)\cdot F.in(\lambda)$ is the $IV$ concatenated with ciphertext blocks $c_i$.

Decryption is similar to encryption.
First, split $c$ into $n+1$ blocks of size $F.in(\lambda)$.
Interpret the first block of $c$ as $IV$.
For each block $c_i$, calculate $r = F.Eval(k, IV+i)$.
Then, calculate the exclusive-or of $r$ and $c_i$ to recover the message block $m_i = c_i \oplus r$.

\begin{Pseudocode}[caption={$SES.Encrypt_F$ algorithm}]
algorithm $SES.Encrypt_F(k, m=m_1 m_2 \dots m_n \in \{0,1\}^{n\cdot F.in(\lambda)})$
Output: Ciphertext $c$
  $\lambda = |k|$
  $IV \leftarrowS \{0,1\}^{F.in(\lambda)}$
  for $i \in \{ 1, 2, \dots, n \}$ do
    $c_i \leftarrow F.Eval(k, (IV+i) \mod 2^{F.in(\lambda)}) \oplus m_i$
  Output $IV||c_1||c_2||\dots||c_n$
\end{Pseudocode}%
\begin{Pseudocode}[caption={$SES.Decrypt_F$ algorithm}]
algorithm $SES.Decrypt_F(k, c=c_0 c_1 \dots c_n \in \{0,1\}^{(n+1)\cdot F.in(\lambda)})$
  Output: cleartext $m$
  $\lambda = |k|$
  $IV \leftarrow c_0$
  for $i \in \{ 1, 2, \dots, n \}$ do
    $m_i \leftarrow F.Eval(k, (IV+i) \mod 2^{F.in(\lambda)}) \oplus c_i$
  Output $m_1||m_2||\dots||m_n$
\end{Pseudocode}%

In \autoref{alg:encode-nd}, we use $SES$ to encrypt the hiddentext message.
Since $IV$ as well as all blocks $c_i$ are indistinguishable from randomness, the entire output of $SES.Encrypt_F$ is indistinguishable from randomness.
In \autoref{alg:decode-nd}, $SES$ is used to decrypt the hiddentext.
Since $SES.Encrypt_F$ yields different ciphertexts on each invocation (even with the same message $m$ and key $k$ because $IV$ is sampled at random on each invocation), an attacker can only distinguish $r \leftarrow SES.Encrypt_F(k,m)$ from randomness if an $IV$ is reused for the same pair $(m,k)$, which is very unlikely.

These modifications improve Meteor's security against SS-CHA adversaries.
Repeated invocations of $EncodeRandomized$ return different stegotexts with overwhelming probability.
Since $SES$ is IND\$-CPA secure, we can, with the same reduction as in Theorem \ref{thm:meteor-secure}, show SS-CHA security against polynomial attackers as long as the same $IV$ is not generated twice, which is very unlikely.

\begin{Pseudocode}[float, caption={
$EncodeRandomized$ algorithm.
This algorithm differs from the original $Encode$ algorithm by using $SES$ to encrypt the message.
The ciphertext (which is indistinguishable from randomness and nondeterministic) is then used to sample from $\mathcal{C}_h$.
}, label={alg:encode-nd}]
algorithm $EncodeRandomized_{\mathcal{C}}^{\beta}(k_{prg}, m, h)$
  Output: Stegotext message $c$
  $c \leftarrow \epsilon,~ i \leftarrow 0,~ n \leftarrow 0$
  $r \leftarrow SES.Encrypt_F(k, m)$
  while $n < |r|$ do
    $c_i \leftarrow Sample_{\mathcal{C}}^\beta(h, r[n: n+\beta])$
    $\mathcal{R} \leftarrow Recover_{\mathcal{C}}^\beta(h, c_i)$
    $n_i \leftarrow LenPrefix^\beta(\mathcal{R})$
    $c \leftarrow c || c_i,~ n \leftarrow n+n_i,~ h \leftarrow h||c_i,~ i \leftarrow i + 1$
  Output $c$
\end{Pseudocode}
\begin{Pseudocode}[float, caption={
$DecodeRandomized$ algorithm.
This algorithm differs from the original $Decode$ algorithm by using $SES$ to decrypt the stegotext.
}, label={alg:decode-nd}]
algorithm $DecodeRandomized_{\mathcal{C}}^{\beta}(k_{prg}, c, h)$
  Output: Plaintext message $m$
  $m \leftarrow \epsilon,~ n \leftarrow 0,~ r \leftarrow \epsilon$
  Parse $c$ as $c_0 || c_1 || \dots || c_{\tau}$
  for $i \in \{ 0, 1, \dots, \tau \}$ do
    $\mathcal{R} \leftarrow Recover_{\mathcal{C}}^\beta(h, c_i)$
    $r_i \leftarrow Prefix^\beta(\mathcal{R})$
    $r \leftarrow r || r_i$
    $h \leftarrow h||c_i$
  $m \leftarrow SES.Decrypt_F(k, r)$
  Output $m$
\end{Pseudocode}